### 2023-04-06 output/group_3_crimes_50m/tables/balance_table.tex
produced all figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_3_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.44 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -0.91 & 1.00 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,927.86 & 0.03 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 706.17 & 0.11 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_50m & 0.35 & 0.07 & 0.01 & -0.01 & 0.48 \\
 & pre_treatment_change_in_group_3_crimes_50m & -0.02 & -0.01 & 0.11 & 0.00 & 0.51 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -153.52 & 0.91 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,794.81 & 0.05 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 608.96 & 0.15 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_3_crimes_50m/tables/pre_treatment_covariate_tests.tex
produced all figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.02 & 0.01 \\
 & pre_treatment_change_in_group_3_crimes_50m & 0.19 & 0.41 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.01 & 0.05 \\
 & poor_share2010 & 0.98 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.00 \\
 & no_cause & 0.29 & 0.95 \\
 & non_payment & 0.61 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
 & hasAttyP & 0.30 & 0.00 \\
 & isEntityD & 0.43 & 0.06 \\
 & isEntityP & 0.49 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_50m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_3_crimes_50m & 0.00 & 0.11 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.44 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.74 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.15 & 0.00 \\
 & no_cause & 0.57 & 0.95 \\
 & non_payment & 0.35 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
 & hasAttyP & 0.61 & 0.00 \\
 & isEntityD & 0.70 & 0.06 \\
 & isEntityP & 0.58 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_4_crimes_100m/tables/pre_treatment_covariate_tests.tex
produced all figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_100m & 1.00 & 0.00 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.15 & 0.22 \\
 & job_density_2013 & 0.51 & 0.10 \\
 & med_hhinc2016 & 0.05 & 0.05 \\
 & poor_share2010 & 0.14 & 0.96 \\
 & popdensity2010 & 0.52 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.86 & 0.00 \\
 & no_cause & 0.92 & 0.95 \\
 & non_payment & 0.83 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.89 & 0.00 \\
 & hasAttyP & 0.88 & 0.00 \\
 & isEntityD & 0.95 & 0.06 \\
 & isEntityP & 0.84 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_100m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_4_crimes_100m & 0.37 & 0.64 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.11 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.05 & 0.00 \\
 & no_cause & 0.37 & 0.95 \\
 & non_payment & 0.02 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.71 & 0.00 \\
 & hasAttyP & 0.78 & 0.00 \\
 & isEntityD & 0.29 & 0.06 \\
 & isEntityP & 0.04 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
produced all figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
 & pre_treatment_change_in_group_4_crimes_500m & 0.00 & 0.48 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.35 & 0.00 \\
 & no_cause & 0.67 & 0.95 \\
 & non_payment & 0.28 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.78 & 0.00 \\
 & hasAttyP & 0.51 & 0.00 \\
 & isEntityD & 0.28 & 0.06 \\
 & isEntityP & 0.92 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_4_crimes_500m & 0.00 & 0.00 \\
 & pre_treatment_change_in_group_4_crimes_500m & 0.01 & 0.03 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.48 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.48 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
 & no_cause & 0.02 & 0.95 \\
 & non_payment & 0.60 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.59 & 0.00 \\
 & hasAttyP & 0.18 & 0.00 \\
 & isEntityD & 0.02 & 0.06 \\
 & isEntityP & 0.36 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-06 output/group_4_crimes_50m/tables/balance_table.tex
produced all figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_4_crimes_50m & 0.02 & 0.01 & 0.01 & -0.00 & 0.43 \\
\cline{1-7}
\textit{Panel B} & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 757.12 & 0.37 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_4_crimes_50m & 0.39 & 0.08 & 0.01 & -0.01 & 0.69 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & -0.01 & 0.17 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -458.26 & 0.75 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & -1,467.75 & 0.04 \\
\cline{1-7}
\textit{Panel C} & non_payment & 0.77 & -0.08 & 0.00 & -0.03 & 0.02 \\
\cline{1-7}
\bottomrule
\end{tabular}
